---
title: "Overview of Gameday"
author: "Michelle Lee"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Gameday}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

# Introduction

Gameday can answer these questions:

- Does my team play today?
- Does my team play tomorrow?
- What is the score for the game today?
- What is the score for the game on Nov 3, 2014?


# Loading the package

```{r}
library(gameday)
```

# gday

`gday` checks whether the specified team played on a specified date. The default for team is the Vancouver Canucks; the default for the date is today's date. For example,

```{r}
gday()
```

If we wanted to check if the Canucks played on 2014-11-03:

```{r}
gday("Canucks", "2014-11-03")
```

Team name is case insensitive:

```{r}
gday("CANUCKS")
```


# scores()

This function returns a data frame with 4 columns: the home team name, away team name, home team score, and away team score. The default for date is today's date. For example:

```{r}
knitr::kable(scores(Sys.Date()), format="markdown")
```

# Pitfalls

`gday` checks whether you have an Internet connection, whether the team name entered is a string, and whether the date entered is in date format. 
`scores` checks whether you have an Internet connection, and whether the date is in proper date format. 

